# Assignment #02

---

## 01. Load Eunomia Cohorts

```{r echo=T, results='hide'}
library(Eunomia)

connectionDetails <- getEunomiaConnectionDetails()
connection <- connect(connectionDetails)
createCohorts(connectionDetails)
```

Check out the data by querying it:

```{r echo=T, results='hide'}
querySql(connection, "SELECT * FROM cohort LIMIT 5;")
```

## 02. Use Feature Extraction

Create per-person covariates for a cohort of interest

```{r echo=T, results='hide'}
library(FeatureExtraction)

cdmDatabaseSchema <- "main"
resultsDatabaseSchema <- "main"

settings <- createDefaultCovariateSettings()

covariateData <- getDbCovariateData(connectionDetails = connectionDetails,
                                    cdmDatabaseSchema = cdmDatabaseSchema,
                                    cohortDatabaseSchema = resultsDatabaseSchema,
                                    cohortTable = "cohort",
                                    cohortId = 1,
                                    rowIdField = "subject_id",
                                    covariateSettings = settings)

summary(covariateData)
```

Create aggregated covariates for a cohort of interest from per-person covariates

```{r echo=T, results='hide'}
covariateData2 <- aggregateCovariates(covariateData)
summary(covariateData2)
```

Create aggregated covariates for a cohort of interest at creation

```{r echo=T, results='hide'}
covariateData3 <- getDbCovariateData(connectionDetails = connectionDetails,
                                     cdmDatabaseSchema = cdmDatabaseSchema,
                                     cohortDatabaseSchema = resultsDatabaseSchema,
                                     cohortTable = "cohort",
                                     cohortId = 1,
                                     covariateSettings = settings,
                                     aggregated = TRUE)
summary(covariateData3)
```

## 03. Show the Features

For per-person covariates (No Table1)

```{r echo=T, results='hide'}
show(covariateData)
```

Table1 for aggregated covariates from per-person covariates

```{r echo=T, results='hide'}
show(covariateData2)
result2 <- createTable1(covariateData2, output = 'one column')
print(result2, row.names = FALSE, right = FALSE)
```

Table1 for aggregated covariates at creation

```{r echo=T, results='hide'}
show(covariateData3)
result3 <- createTable1(covariateData3, output = 'one column')
print(result3, row.names = FALSE, right = FALSE)
```

## 04. Create a Cohort using SQL

### Download CSV files

Here we're downloading all the files from the [MIMIC IV demo dataset](https://physionet.org/content/mimic-iv-demo-omop/0.9/1_omop_data_csv/#files-panel).

*Note: The downloaded files must be the ones related to the [OMOP-CDM data model](https://ohdsi.github.io/TheBookOfOhdsi/CommonDataModel.html).*

```{r echo=T, results='hide'}
download_path = '/home/ohdsi/workdir/src/assignment_1_downloads'
base_url = 'https://physionet.org/files/mimic-iv-demo-omop/0.9/1_omop_data_csv'
files = c('care_site.csv', 'cdm_source.csv', 'cohort.csv', 'cohort_definition.csv', 'condition_era.csv', 'condition_occurrence.csv',  'cost.csv', 'device_exposure.csv', 'dose_era.csv', 'drug_era.csv', 'drug_exposure.csv', 'fact_relationship.csv', 'location.csv', 'measurement.csv', 'metadata.csv', 'note.csv', 'note_nlp.csv', 'observation.csv', 'observation_period.csv', 'payer_plan_period.csv', 'person.csv', 'procedure_occurrence.csv', 'provider.csv', 'specimen.csv', 'visit_detail.csv', 'visit_occurrence.csv')
lapply(files, function(file){
  download_url = paste0(base_url, '/', file, '?download')
  file_path = paste0(download_path, '/', file)
  
  download.file(download_url, file_path)
})
```

## Create the Database

Then we create the database (DB) with the [RSQLite](https://cran.r-project.org/web/packages/RSQLite/vignettes/RSQLite.html) package.

```{r echo=T, results='hide'}
library(DBI)
source = '/home/ohdsi/workdir/src/assignment_1_downloads'
files = list.files(source)
# Create DB.
mimic_iv_db = dbConnect(RSQLite::SQLite(), 'mimic_iv_demo.sqlite')
lapply(files, function(file){
  table_name = substr(file, 1, nchar(file) - 4)
  file_path = paste0(source, '/', file)
  data = read.csv(file_path)
  dbWriteTable(mimic_iv_db, table_name, data, overwrite=TRUE)
})
dbDisconnect(mimic_iv_db)
```