# Assignment #01

---

## 1. Download CSV files

Here we're downloading all the files from the [MIMIC IV demo dataset](https://physionet.org/content/mimic-iv-demo-omop/0.9/1_omop_data_csv/#files-panel).

*Note: The downloaded files must be the ones related to the [OMOP-CDM data model](https://ohdsi.github.io/TheBookOfOhdsi/CommonDataModel.html).*

```{r echo=T, results='hide'}
download_path = '/home/ohdsi/workdir/src/assignment_1_downloads'
base_url = 'https://physionet.org/files/mimic-iv-demo-omop/0.9/1_omop_data_csv'

files = c('care_site.csv', 'cdm_source.csv', 'cohort.csv', 'cohort_definition.csv', 'condition_era.csv', 'condition_occurrence.csv',  'cost.csv', 'device_exposure.csv', 'dose_era.csv', 'drug_era.csv', 'drug_exposure.csv', 'fact_relationship.csv', 'location.csv', 'measurement.csv', 'metadata.csv', 'note.csv', 'note_nlp.csv', 'observation.csv', 'observation_period.csv', 'payer_plan_period.csv', 'person.csv', 'procedure_occurrence.csv', 'provider.csv', 'specimen.csv', 'visit_detail.csv', 'visit_occurrence.csv')

lapply(files, function(file){
  download_url = paste0(base_url, '/', file, '?download')
  file_path = paste0(download_path, '/', file)
  
  download.file(download_url, file_path)
})
```

## Create the Database

Then we create the database (DB) with the [RSQLite](https://cran.r-project.org/web/packages/RSQLite/vignettes/RSQLite.html) package.

```{r echo=T, results='hide'}
library(DBI)

source = '/home/ohdsi/workdir/src/assignment_1_downloads'
files = list.files(source)

# Create DB.
mimic_iv_db = dbConnect(RSQLite::SQLite(), 'mimic_iv_demo.sqlite')

lapply(files, function(file){
  table_name = substr(file, 1, nchar(file) - 4)
  file_path = paste0(source, '/', file)
  data = read.csv(file_path)
  dbWriteTable(mimic_iv_db, table_name, data, overwrite=TRUE)
})

dbDisconnect(mimic_iv_db)
```

Finally we can check out the data by querying it: 

```{r echo=T}
library(DBI)

mimic_iv_db = dbConnect(RSQLite::SQLite(), 'mimic_iv_demo.sqlite')

dbGetQuery(mimic_iv_db, 'SELECT * FROM care_site LIMIT 5')

dbDisconnect(mimic_iv_db)
```


```{r include=FALSE}
if (!"DataQualityDashboard" %in% rownames(installed.packages())) {
  install.packages("devtools")
  devtools::install_github("OHDSI/DataQualityDashboard")
}

download.file(
  "https://physionet.org/files/mimic-iv-demo-omop/0.9/3_data_quality_dashboard_files/results_MIMICIVdemo210426.json?download", 
  file.path(getwd(), "results_MIMICIVdemo210426.json")
)

```

## 4. Data Quality DashBoard

Execute Data quality Daschboard application using file results_MIMICIVdemo210426.json.

```{r echo=TRUE}
library("DataQualityDashboard")

DataQualityDashboard::viewDqDashboard(
  jsonPath = file.path(
    getwd(), 
    "results_MIMICIVdemo210426.json"
  )
)

```
---
